Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-16 tex/MesnardoBarba2019.tex
new text mentioning F&A costs

Universities and national laboratories spend millions of dollars to deploy and maintain on-site high-performance computing (HPC) clusters.
At the George Washington University, we have access to a university-managed HPC cluster called Colonial One.
The cluster is now $6$ years old and approaching its end-of-life.
On average, its computational resources are idle $9\%$ of the time and unavailable to users for roughly 5 days a year (due to maintenance).
Administrators of the cluster have been recently considering integrating cloud-computing platforms in the research-computing portfolio. 
Over the past decade, cloud-computing platforms have rapidly evolved, now offering solutions for scientific applications.
From a user's point of view, a cloud platform offers great flexibility (hardware and virtual machines) with instantaneous availability of infinite (in appearance) computational resources.
No more waiting time in job-submission queues!
This promises to greatly facilitate code development, debugging, and testing. Resources allocated on the cloud are released as soon as the job is done, avoiding paying for idle time.
On a public-cloud platform---such as Microsoft Azure, Google Cloud, Amazon AWS---with a "pay-as-you-go" type of subscription, a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters. 
Cost models that make sense for researchers, labs, and universities are still unclear. 
Yet, this information is key when making a decision to adopt a cloud workflow for research. 
We report here what we have learned from nearly two years of using cloud computing for our computational fluid dynamics (CFD) simulations, with the hope that it will shed some light on the costs and benefits, and help others considering using cloud computing for their research.

@@

>>>>

Universities and national laboratories spend millions of dollars to deploy and maintain on-site high-performance computing (HPC) clusters.
At the George Washington University, we have access to a cluster called Colonial One.
The cluster is now $6$ years old and approaching its end-of-life.
On average, its computational resources are idle $9\%$ of the time and unavailable to users for roughly 5 days a year (due to maintenance).
Administrators of the cluster have been recently considering integrating cloud-computing platforms in the research-computing portfolio. 
Over the past decade, cloud-computing platforms have rapidly evolved, now offering solutions for scientific applications.
From a user's point of view, a cloud platform offers great flexibility (hardware and virtual machines) with instantaneous availability of infinite (in appearance) computational resources.
No more waiting time in job-submission queues!
This promises to greatly facilitate code development, debugging, and testing. Resources allocated on the cloud are released as soon as the job is done, avoiding paying for idle time.
On a public-cloud platform---such as Microsoft Azure, Google Cloud, Amazon AWS---with a "pay-as-you-go" type of subscription, a user directly sees how much it costs to run a scientific application, while such information usually remains obscure to the end-user on university-managed clusters. 
Cost models that make sense for researchers, labs, and universities are still unclear. 
Yet, this information is key when making a decision to adopt a cloud workflow for research. 
We report here what we have learned from nearly two years of using cloud computing for our computational fluid dynamics (CFD) simulations, with the hope that it will shed some light on the costs and benefits, and help others considering using cloud computing for their research.

@@

In this work, we show that public cloud resources are today able to deliver similar performances to a university-managed cluster, and thus can be regarded as a suitable solution for research computing.
But in addition to performance, researchers also worry about cost.
We share the actual costs incurred to run two- and three-dimensional CFD simulations  using cloud services with a pay-as-you-go model, and report on reduced costs possible with reserved instances.
Universities (and possibly funding agencies) may obtain even more favorable pricing through bids or medium-term contracts.
Researchers thinking of adding cloud computing to proposal budgets might encounter other barriers, however.
For example, some universities exempt large equipment purchases from indirect (facilities and administrative, F\&A)  costs, while they may add these overhead rates to cloud purchases. 
Until these internal policies are adjusted, cloud computing may not be adopted widely.
